---
title: "Applied Econometrics"
site: workflowr::wflow_site
output:  
  html_document
---

```{r eval=T, echo=F, warning=F, message=F}
# Packages
library(tidyverse)
library(readxl)
```

```{r eval=T, echo=F, warning=F}
# Data Import
corr_1 <- read_excel("data/corr_1.xlsx")
```

# Setting Up

## Packages 
* **tidyverse** - basic package for data wrangling

* **readxl** - allows inputs of excel files

* **readr** - allows inputs of text files

* **stargazer** - better organized regression outputs 

## Output Tables

# Initial Statistics

## Correlation

### One Variable

Correlation is the strength of linear assosciation. It can be sensitive to outliers.
```{r eval=T, echo=T}
cor <- corr_1 %>% 
  summarise(r=cor(X, Y)) %>% 
  pull(r)
cor
```
Correlations can also be visualized through scatterplots which are the foundation of econometric analysis. 
```{r eval=T, echo=T, message=F}
ggplot(corr_1, aes(x=X, y=Y))+
  geom_point(alpha=0.5)+
  geom_smooth(method = "lm", se=F)
```
```{r eval=T, echo=F}
remove(corr_1, cor)
```

### Multiple Variable

# Simple Linear Regression

## Visualizing Assumptions

## Dummy Variables

# Hypothesis Testing








