---
title: "Latex"
site: workflowr::wflow_site
output:  
  html_document
---

# Display

## Inline form
```{r eval=F, echo=T}
$a+b=3$
```
Inline expression is simply $a+b=3$.

## Display form
```{r eval=F, echo=T}
$$a+b=3$$
```
Display form is double $$a+b=3$$

# Math Notations

## Sub/Super-script
```{r eval=F, echo=T}
Subscript: $X_{i}$. Superscript: $X^{2}$. Combined: $X^{2}_{i}$
```
Subscript $X_{i}$, and superscript $X^{2}$. Combining them will be $X^{2}_{i}$.

## Square root
```{r eval=F, echo=T}
$\sqrt{b^2-4ac}$
```
Example: $\sqrt{b^2-4ac}$

## Fractions
```{r eval=F, echo=T}
$\frac{a}{b+c-1}$
```
Example: $\frac{a}{b+c-1}$

## Great/Less Equals
```{r eval=F, echo=T}
$a \geq 20$, $a > 20$ $a \leq 20$, $a \neq 20$
```
Example: $a \geq 20$, $a > 20$ $a \leq 20$, $a \neq 20$

## Summations
```{r eval=F, echo=T}
$\sum_{i=1}^{n} (x_i+1)^2$
```
Example: $\sum_{i=1}^{n} (x_i+1)^2$

## Integration
```{r eval=F, echo=T}
$\int_0^{2\pi} \sin x~dx$
```
Example: $\int_0^{2\pi} \sin x~dx$

# Brackets
```{r eval=F, echo=T}
$[z\{2a + b(c+1)\}]$
```
Example: $[z\{2a + b(c+1)\}]$

Brackets that fit requires `\left` and `\right`
```{r eval=F, echo=T}
$\left (\frac{a}{b+1} \right)$
```
Example: $\left (\frac{a}{b+1} \right)$

# Align
You need to use `\begin{align}` and `\end{align}`.
```{r eval=F, echo=T}
$$
\begin{align}
2a+4b &=10 && \text{Equation 1}\\
2(a+2b) &= 10\\
a+2b &= 5
\end{align}
$$
```
$$
\begin{align}
2a+4b &=10 && \text{Equation 1}\\
2(a+2b) &= 10\\
a+2b &= 5
\end{align}
$$

# Matrix
```{r eval=F, echo=T}
$$\mathbf{X} = \left[\begin{array}
{rrr}
1 & 2 & 3 \\
4 & 5 & 6 \\
7 & 8 & 9
\end{array}\right]
$$
```
$$
\mathbf{X} = \left[\begin{array}
{rrr}
1 & 2 & 3 \\
4 & 5 & 6 \\
7 & 8 & 9
\end{array}\right]
$$

# Optimization
```{r eval=F, echo=T}
$$
\underset{q>0}{\text{max}} [V(q)+\delta_t + V'(q)]
$$
```
$$
\underset{q>0}{\text{max}} [V(q)+\delta_t + V'(q)]
$$








